\plaintitle

### 2016-09-21 drafts/labor/cases.tex
added a ref shortname
citation fixes

\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,    overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

@@

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work,  saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',  parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,  and indeed the study of factory and mass manufacturing labor through the \nth{20} century,  substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,  and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work,  including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''
\cite{thompson1913time}.

Broken down in this way, work could grow to unprecedented scales,  but the quality of the work would remain relatively variable
\cite{murray1983decentralisation}.
Textile work being a salient example,  it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work
\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,  manageable routines that could be taught relatively easily,  and whose work output could be evaluated in abstraction from the rest of the work
\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,  but a single very narrowly defined action that needed to be done on every car
\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,  ``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''
\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),  can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,  facilitating evaluation and parallelization
\cite{writingMicroTasks}.
By decomposing and recomposing tasks,  and in particular by assigning similarly natured work to the same workers,  workers could become ``experts'' in a small aspect of the work that they did,  speeding their work dramatically
\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage
\cite{rogstadius2011assessment}.

>>>>

%\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,    overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

@@

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work,  saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',  parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work~\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,  and indeed the study of factory and mass manufacturing labor through the \nth{20} century,  substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,  and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work,  including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''~\cite{thompson1913time}.

Broken down in this way, work could grow to unprecedented scales,  but the quality of the work would remain relatively variable~\cite{murray1983decentralisation}.
Textile work being a salient example,  it took time for workers to acquire sufficient skill
to do every aspect of the work so that the garment would be accepted by the company soliciting that work~\cite{vezina1992light}.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,  manageable routines that could be taught relatively easily,  and whose work output could be evaluated in abstraction from the rest of the work~\cite{restructuringPieceworkBaker}.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,  but a single very narrowly defined action that needed to be done on every car~\cite{towardsGlobalFordism}.
By the mid--\nth{20} century, \citeauthor{schoenberger1988fordism} writes,  ``\dots~the intensification of the labor process is argued to have hit mental, physical, and social limits.''~\cite{schoenberger1988fordism}.

This approach, ``Fordism'' (and its better--known contemporary ``Taylorism'' of similar ethos),  can be seen today in crowd work and on--demand labor through the application of micro--tasks.
\citeauthor{writingMicroTasks} highlight some of the advantages of breaking work into pieces,  facilitating evaluation and parallelization~\cite{writingMicroTasks}.
By decomposing and recomposing tasks,  and in particular by assigning similarly natured work to the same workers,  workers could become ``experts'' in a small aspect of the work that they did,  speeding their work dramatically~\cite{delayAndOrderLasecki}.
Perhaps more important, however, was that
the breaking down of work into tasks has made it more practical to evaluate work at each stage~\cite{rogstadius2011assessment}.

### 2016-09-21 drafts/labor/complexity.tex
citation fixes

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless crowdsourcing can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers
\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks
\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling
\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants \cite{Lasecki:2013:CCC:2501988.2502057},
medical data interpreters \cite{Lasecki:2013:CCC:2501988.2502057}, and
idea generation \cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing workflows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce
\cite{crowdForgeKittur} or
sequence alignment algorithms
\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
% \ali{We could quote \citeauthor{storiesIraniSilberman} and say ``human APIs'',
% but that gets a little critique--y, and we might want to save that for later.}
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

It is now clear that this approach works with focused complex tasks, but
the broader wicked problem that each complex goal represents remains unsolved
\cite{rittel1973dilemmas}.
As a first example,
idea generation shows promise
\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation
\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible
\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,
      writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering \cite{chilton2013cascade},
categorization \cite{andre2014crowd}, and
outlining \cite{luther2015crowdlines}
are possible, but there is no general solution for sensemaking.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.
%  and
% other crowdsourced goals such as addressing climate change
% \cite{introne2011climate}.

Restricting attention to non--expert, microtask workers proved limiting.
So, \citeauthor{foundry} introduced the idea of crowdsourcing with
online paid \textit{experts} from platforms such as Upwork.
Expert crowdsourcing enables access to a much broader set of workers,
for example designers and programmers.
The same ideas can then be applied to expert ``macro--tasks''
\cite{cheng2015break,haas2015argonaut}, enabling the crowdsourcing of goals such as user--centered design \cite{foundry},
programming \cite{latoza2014microtask,Fast2016,Chen2016}, and
mentorship \cite{suzukiAtelier}.
However, there remains the open question of
how complex the work outcomes from expert crowds can be.

@@

\topic{\citeauthor{grier2013computers} gives early accounts of
a piecework strategy in Airy's creation of
the British Nautical Almanac
\cite{grier2013computers}.}
Airy's goal was complex
--- mathematical calculations to produce tables that would
allow sailors to locate themselves by starlight from sea.
Many of his contributors did not have high--level mathematical training,
so Airy broke down the task into simpler calculations and
distributed them by mail,
accomplishing the complex goal through piecework tasks that paid little.

However, when piecework entered the American economy,
it was not used for complex work.
One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry
\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated New York City
\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage \cite{burton1899commercial} and
management regimes \cite{norton1900textile}
rather than training.

@@

\topic{Piecework was limited to tasks that could be clearly evaluated.}
For example, the roles required to facilitate piecework in the early \nth{20} century included ``piecework clerks, inspectors, and `experts'''~\cite{10.2307/23702539}.
\citeauthor{hart2016rise} argues that evaluation causes an ultimate complexity limit:
at some point, evaluating multidimensional work for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity [\ldots]
then a piecework system is likely to encourage
an over--emphasis on quantity produced and an under--emphasis on quality''
\cite{hart2016rise}.
Complex work, which is often subjective to evaluate, falls victim to this criteria.

\topic{This focus on measurement and tracking had consequences.}
\citeauthor{10.2307/23702539} suggests that the first sparks of scientific management
could be found in piecework:
the approach of paying workers for each piece of output necessitated
the rigorous tracking, measurement, and training of workers
for which scientific management became famous
\cite{10.2307/23702539}.
If true, 
the concurrent upswing of
scientific management and Fordism
through the first two--thirds of the \nth{20} century
alongside piecework was not only understandable, but predictable
\cite{hart2013rise}.

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} were amenable to piecework.}
Researchers detail three organizational criteria.
First, \citeauthor{Brown01041990} argues that
piecework ``is less likely in jobs with a variety of duties than in
jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{SJOE:SJOE371} points out the phenomenon here as a market effect:
``in an environment with multi--tasking,
pay schemes based on tightly specified performance may
induce workers to neglect tasks that are less easy to measure''
\cite{SJOE:SJOE371}.
Second,
complexity was limited by access to capital to create the necessary infrastructure.
As \citeauthor{10.2307/23702539} reports,
only the largest and most wealthy railroads had the resources
necessary
% ``pay the overhead involved in installing work reorganization''
~\cite{10.2307/23702539}.
Third, organizations required capable managers in charge of the pieceworkers.
The West Virginia mines, for example, hired foremen 
to be the intermediary between upper management and the workers~\cite{10.2307/2118435}.
These foremen were responsible for allocating resources and
understanding when and how to modify work as necessary
\cite{wray1949marginal}.
So, in sum,
organizations historically could only take advantage of piecework if they had
homogeneous work to be done,
access to capital to purchase the necessary equipment, and
the ability to hire people who could serve as intermediaries between pieceworkers and management.

\topic{The research seems to suggest that it was difficult to apply piecework to more skilled work,
particularly because maximizing the advantages of piecework seemed to reward
smaller, more constrained, more narrowly--trained tasks, and only in organizations that could pay for the equipment and people to enable it.}
For most of the \nth{19} century,
piecework was applied almost exclusively to farm and textile work.
Work was simple and widely understood
--- farm workers didn't need to be trained on how to plow fields, or birth foals;
seamstresses knew how to sew together denim
\cite{10.2307/2338394,riisOtherSideLives}.

@@

% \topic{Digital media have expanded the scope of
% viable piecework by pushing drastically on the limits
% cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity
\cite{Brown01041990}.
Given the flourishing of on--demand labor platforms such as
Uber, AMT, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the Internet has trivialized
the costs and challenges of the earlier limiting factors
because technology makes it easier
\begin{inlinelist}
\item for workers to do complex work without training,
\item to manage workers in doing complex work, and 
\item to create the infrastructure necessary to manage the workers.
\end{inlinelist}

\topic{Technology increases non--experts' levels of expertise by giving access to information that would otherwise be unavailable.}
For example, taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity with the city's roads.
This test is so challenging that veteran drivers exhibit significantly larger
the regions of the brain associated with spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625,
      skok2000managing,Woollett1407,woollett2011acquiring}.
In contrast, with on--demand platforms such as Uber, services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to operate profesionally~\cite{silva2013traffic,hind2014outsmarting}.
Other examples include search engines enabling information retrieval, and word processors enabling spelling and grammar checking.
By augmentating the human intellect~\cite{engelbart2001augmenting}, computing has shifted the complexity of work that is possible without training.

@@

\subsubsection{\implication}
% \topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
% it also signals some of the ultimate limitations of crowd work and piecework in general.}
% While the threshold preventing task requesters from utilizing piecework
% has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
% \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
% If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
% we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation \cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework \cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

>>>>

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless crowdsourcing can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers~\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling~\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants \cite{Lasecki:2013:CCC:2501988.2502057},
medical data interpreters \cite{Lasecki:2013:CCC:2501988.2502057}, and
idea generation \cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing workflows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce~\cite{crowdForgeKittur} or
sequence alignment algorithms~\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
% \ali{We could quote \citeauthor{storiesIraniSilberman} and say ``human APIs'',
% but that gets a little critique--y, and we might want to save that for later.}
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

It is now clear that this approach works with focused complex tasks, but
the broader wicked problem that each complex goal represents remains unsolved~\cite{rittel1973dilemmas}.
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,
      writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering \cite{chilton2013cascade},
categorization \cite{andre2014crowd}, and
outlining \cite{luther2015crowdlines}
are possible, but there is no general solution for sensemaking.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.
%  and
% other crowdsourced goals such as addressing climate change
% \cite{introne2011climate}.

Restricting attention to non--expert, microtask workers proved limiting.
So, \citeauthor{foundry} introduced the idea of crowdsourcing with
online paid \textit{experts} from platforms such as Upwork.
Expert crowdsourcing enables access to a much broader set of workers,
for example designers and programmers.
The same ideas can then be applied to expert ``macro--tasks''~\cite{cheng2015break,haas2015argonaut}, enabling the crowdsourcing of goals such as user--centered design \cite{foundry},
programming \cite{latoza2014microtask,Fast2016,Chen2016}, and
mentorship \cite{suzukiAtelier}.
However, there remains the open question of
how complex the work outcomes from expert crowds can be.

@@

\topic{\citeauthor{grier2013computers} gives early accounts of
a piecework strategy in Airy's creation of
the British Nautical Almanac~\cite{grier2013computers}.}
Airy's goal was complex
--- mathematical calculations to produce tables that would
allow sailors to locate themselves by starlight from sea.
Many of his contributors did not have high--level mathematical training,
so Airy broke down the task into simpler calculations and
distributed them by mail,
accomplishing the complex goal through piecework tasks that paid little.

However, when piecework entered the American economy,
it was not used for complex work.
One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage \cite{burton1899commercial} and
management regimes \cite{norton1900textile}
rather than training.

@@

\topic{Piecework was limited to tasks that could be clearly evaluated.}
For example, the roles required to facilitate piecework in the early \nth{20} century included ``piecework clerks, inspectors, and `experts'''~\cite{10.2307/23702539}.
\citeauthor{hart2016rise} argues that evaluation causes an ultimate complexity limit:
at some point, evaluating multidimensional work for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity [\ldots]
then a piecework system is likely to encourage
an over--emphasis on quantity produced and an under--emphasis on quality''~\cite{hart2016rise}.
Complex work, which is often subjective to evaluate, falls victim to this criteria.

\topic{This focus on measurement and tracking had consequences.}
\citeauthor{10.2307/23702539} suggests that the first sparks of scientific management
could be found in piecework:
the approach of paying workers for each piece of output necessitated
the rigorous tracking, measurement, and training of workers
for which scientific management became famous~\cite{10.2307/23702539}.
If true, 
the concurrent upswing of
scientific management and Fordism
through the first two--thirds of the \nth{20} century
alongside piecework was not only understandable, but predictable~\cite{hart2013rise}.

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} were amenable to piecework.}
Researchers detail three organizational criteria.
First, \citeauthor{Brown01041990} argues that
piecework ``is less likely in jobs with a variety of duties than in
jobs with a narrow set of routinized duties''~\cite{Brown01041990}.
\citeauthor{SJOE:SJOE371} points out the phenomenon here as a market effect:
``in an environment with multi--tasking,
pay schemes based on tightly specified performance may
induce workers to neglect tasks that are less easy to measure''~\cite{SJOE:SJOE371}.
Second,
complexity was limited by access to capital to create the necessary infrastructure.
As \citeauthor{10.2307/23702539} reports,
only the largest and most wealthy railroads had the resources
necessary
% ``pay the overhead involved in installing work reorganization''
~\cite{10.2307/23702539}.
Third, organizations required capable managers in charge of the pieceworkers.
The West Virginia mines, for example, hired foremen 
to be the intermediary between upper management and the workers~\cite{10.2307/2118435}.
These foremen were responsible for allocating resources and
understanding when and how to modify work as necessary~\cite{wray1949marginal}.
So, in sum,
organizations historically could only take advantage of piecework if they had
homogeneous work to be done,
access to capital to purchase the necessary equipment, and
the ability to hire people who could serve as intermediaries between pieceworkers and management.

\topic{The research seems to suggest that it was difficult to apply piecework to more skilled work,
particularly because maximizing the advantages of piecework seemed to reward
smaller, more constrained, more narrowly--trained tasks, and only in organizations that could pay for the equipment and people to enable it.}
For most of the \nth{19} century,
piecework was applied almost exclusively to farm and textile work.
Work was simple and widely understood
--- farm workers didn't need to be trained on how to plow fields, or birth foals;
seamstresses knew how to sew together denim~\cite{10.2307/2338394,riisOtherSideLives}.

@@

% \topic{Digital media have expanded the scope of
% viable piecework by pushing drastically on the limits
% cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity~\cite{Brown01041990}.
Given the flourishing of on--demand labor platforms such as
Uber, AMT, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the Internet has trivialized
the costs and challenges of the earlier limiting factors
because technology makes it easier
\begin{inlinelist}
\item for workers to do complex work without training,
\item to manage workers in doing complex work, and 
\item to create the infrastructure necessary to manage the workers.
\end{inlinelist}

\topic{Technology increases non--experts' levels of expertise by giving access to information that would otherwise be unavailable.}
For example, taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity with the city's roads.
This test is so challenging that veteran drivers exhibit significantly larger
the regions of the brain associated with spatial functions such as navigation~\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625,
      skok2000managing,Woollett1407,woollett2011acquiring}.
In contrast, with on--demand platforms such as Uber, services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to operate profesionally~\cite{silva2013traffic,hind2014outsmarting}.
Other examples include search engines enabling information retrieval, and word processors enabling spelling and grammar checking.
By augmentating the human intellect~\cite{engelbart2001augmenting}, computing has shifted the complexity of work that is possible without training.

@@

\subsubsection{\implication}
% \topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
% it also signals some of the ultimate limitations of crowd work and piecework in general.}
% While the threshold preventing task requesters from utilizing piecework
% has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
% \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
% If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
% we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation \cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework \cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors~\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.
